\documentclass[char]{iron}
\begin{document}
\name{\cFakePriest{}}

Ok, ok, you can do this.  You've been to a few weddings before.  The nice
person who gave you a way out gave you some books you've tried to read.
Everything's going to be fine.  Just don't think about what they'll
do to you when you get caught.

You're totally going to get caught, aren't you.

See, you're \cFakePriest{\real{\full}}.  Fire caste soldier.  This
wasn't such a bad gig a year or two ago.  \sHomeCountry{} was at
peace.  Sure, drills and such are work.  You have to deal with guard
duty, put up with the commanders, sleep in the barracks.  But then,
when you go to the tavern in the evenings, it's lots of fun.  The pay's
good, you stay in great shape, you have good stories.  It was a good
gig.

But then \sMulanCountry{} decided it'd be a great idea to mass troops,
to make some threats, to try some covert operations.  Sure, that great
hero \cMulan{} or whatever stopped their invasion, but things are still
tense at the border.  Fighting could break out any time.  And you almost
died last battle.  Your fort's liable to see heavy fighting if there
is a straight-up invasion.  And if your generals decide to take the fight
to them, you'll likely get assigned to front guard.  Not odds you like.
Not odds you like at all.

So, maybe you had a lot to drink.  And maybe the other soldiers were taunting
you a bit, goading you on, telling stories about how horrible and bloody
battle is.  And at some point, you really just wanted to be anywhere else
but a border fort.

So you ran.

Of course, in the morning, your situation hit you.  Desertion is not looked
on nicely by the military.  Your family's all Fire caste; none of them
would take you in.  You had nowhere to go.

For a while, you just kept to the wilderness.  Your military training prepared
you to survive on your own for a while.  But you couldn't live like that
forever.  So you headed for the capital.  Maybe you could blend in there.

But by the time you got there, you still didn't really have a plan.  You
needed a place to live.  An income other than fighting.  But what could you
do?

You were standing by one of the fountains when you hear the clank of armor.
A cluster of soldiers, moving directly towards you!  You panicked and
ran into the building nearby, some temple.  Seeing a Water cleric there,
you called ``Sanctuary!''  They sat you down and listened to your story.

And then the cleric, \cRealPriest{\real{\full}}, made a wild proposal:
switch places.  They'd pull some strings to get around that whole ``desertion''
thing and go back to the border as you, and you could stay here as a cleric.
It sounded wonderful, and you accepted without a second thought.

Of course, you hadn't quite gotten at the time that \cRealPriest{\real{\first}}
was actually the Head Cleric for all \sHomeCountry{}.

They helped you with a disguise, gave you some pointers, left you some
books to read, and then left.  And you were adrift.  You couldn't make
heads or tails of the books.  And then people found you: clerics,
messengers, servants.  Asking you questions.  Asking why you hadn't led
services.  Asking if you felt all right.  You claimed illness, bumbled through
the questions as best you could, tried not to tip anyone off.  You avoided
people as much as possible, but there was only so much you could put off.

And what you cannot at all put off is the Convergence.  You never knew
much about it beyond vague stories, before, but apparently it's some
sort of once-in-a-lifetime mystical event that can reshape your whole
society.  There's all this ceremony that you have no idea about.  There's
something about people making butterflies out of elemental gems to
reshape the caste system?  That seems like it has all sorts of failure modes.
If the Fire caste gets stronger, they'll probably get \sHomeCountry{}
into all sorts of wars.  You don't wish the horror of war on anybody.  But
if the Fire caste falls in the social hierarchy, then life will suck for
the ordinary soldiers like you were even more.  That doesn't sound good either.
It'd probably be safest just to leave things as they are.

Meddling with the caste system isn't enough for these people, though.
They also want to change the sacred, codified, enshrined traditions of
\sHomeCountry{}.  That's maybe not \emph{so} bad, in theory.  But one
of those traditions is the ban on using fire magic in warfare.  War's
horrible enough for soldiers when it's just swords and bows.  If we
start using fire magic, and our enemies start using it back, it'd just
be horrendous.  No, that's one tradition that needs to stand firm.

You guess you're supposed to be orchestrating both of those ceremonies,
but that's not all.  Apparently marriages in the first half hour after the
Realignment are supposed to be particularly auspicious, so there's going
to be a lot of demand for your services officiating.  But there are all
these rules about weddings, and if you get them wrong everyone's going
to know you're a fake.

The big rule for weddings is all about caste: someone can only marry
someone else in the same caste or a caste that's adjacent in the
social hierarchy.  (You think there's even a bit in the ceremony
where you're supposed to confirm the parties' identities and castes.)
So, with the current caste hierarchy, someone in
the Fire caste could marry someone from the Air or Water caste, but
not someone from the Earth caste.  Except, it's inauspicious to marry
right before the Realignment, so these marriages will all be after the
Realignment. Thus, who can marry whom will be based on the new ordering
of the castes, after everyone's changed the caste system with their
magic gem butterflies.

Were the gods drunk when they set all this up?  Whatever, it's worlds
better than getting shot at.  It can't be that hard to bluff your way
through officiating the most important religious ceremonies of a
century among some of the most important people in all
\sHomeCountry{}.  Knowing that if you mess up, everyone'll know you're
a fake.  And you'll probably get taken back to the fort and
court-martialed for desertion.

Just don't let anyone see how scared you are.

\begin{itemz}[Goals]
\item Do whatever you need to to stay out of the war.
\item Keep your position as Head Cleric by keeping the Convergence running
  smoothly, performing auspicious marriages, and making sure no forbidden
  marriages take place.
\item For the Realignment, maintain the status quo, especially as regards
  to the position of Fire.
\item Maintain the tradition against the use of fire magic in warfare;
  war's hell enough as it is.
\end{itemz}

\begin{contacts}
\contact{\cRealPriest{}}  Actually \cRealPriest{\real{\full}}, the Water cleric
  you traded places with.
\contact {\cRoyalty{}} The monarch's here, of course.  They must
  work with the Head Cleric all the time.  What if they find you out?
\contact{\cGuildmaster{}} The Guildmaster of the Water caste, and the leader of Water's delegation to the Convergence.
\contact{\cTrickster{}} A less prestigious but still successful merchant, here to represent Water as well.
\contact{\cHotPerson{}} An irresistibly attractive delegate. But alas, their status as a noble of Air places them forever out of your reach\ldots{}
\end{contacts}

\end{document}
