\documentclass[char]{iron}
\begin{document}
\name{\cLieutenant{}}

Glory.  Glory rightfully earned.  Glory against a worthy adversary.  That's
what you've been working towards your whole adult life.  That's what you've
sought.  And now, when you finally deserve it, to get passed over?  That's
the ultimate insult.

You were born and raised Water caste.  You learned to count beans and balance
accounts, organize caravans and negotiate prices.  Useful enough skills.
Practical.  Boring.  Stifling.

There's a reason the Fire caste is above Water.  What does Water risk?
A few disks of metal?  The ability to buy furnishings for your sitting
room?  What value is there in that?  In the trappings of finery bought
with numbers?

Fire soldiers risk their bone and blood, their very lives, to earn
glory fighting for their home and country.  What could be more worthy
than that?  And yet, you were born to merchants, doomed to the quiet
suffocation of the Water caste.

You weren't willing to accept that.

You took some gold from your mother's desk, bought some things, and stole
off.  You heard there was unrest at the border with \sMulanCountry{},
so you went to a fort there.  You presented yourself as \cLieutenant{},
the youngest child of a provincial Fire family sent to aid in the war.
They were happy to put you through training.

Training wasn't easy work, far from it.  You were used to sitting at a desk
with a quill and ink.  You weren't decadent the way those Air weaklings get,
but you'd never been through a Fire training regimen.  The other soldiers
laughed at your weakness and panting.  But you didn't let it get to you.
You practiced extra hours, late into the evening when the other soldiers were
resting, lifting stones, climbing stairs, and doing drills to get your
strength up.

One evening, you noticed you weren't the only one doing extra training.
\cMulan{\intro} seemed to be in a similar situation to the one you were in.  Seeing
your attention, they asked you if you wanted to spar.  Soon, you were
training together every evening.  You could help them out, give them
tips on how to improve.  And it was good to have someone you could talk to
who didn't make you feel like a weakling.

You wondered about \cMulan{\first}'s story, but they never seemed inclined
to talk much about their past.  Until one evening, they slipped.  They'd
mentioned being from a branch of the \cMulan{\last} family in the capital,
so when they told a story about being out in the fields with one of their
siblings, it stood out.  When you asked about it, \cMulan{\first} stared
at you like a kid in the larder.  But after a moment, they came clean.
They told you that they were actually Earth caste, in disguise to join
the army.  You were impressed; they'd done a good job with the disguise.
And then you decided to take a calculated risk, and told them your
story.  The mutual confidence brought you even closer together, and
you became staunch allies.

Then one night, after the \sMulanCountryPeople{} got bold enough to
test some of the border forts, your division was out scouting near an
enemy encampment.  You were on night guard duty.  \cMulan{\first} said
they heard movement.  The other guards wouldn't listen, but you went
with \cMulan{\first} to investigate.  And you found a whole troupe of
\sMulanCountryPeople{}, dressed to blend in in the dark, sneaking past the
border.  You knew at once that this was important.  If they weren't stopped,
they could wreak untold havoc, terrorizing the countryside or assassinating
leaders.  This was your chance.  You told \cMulan{\first} to track them
and leave a trail while you went for help.  You wasted no time in rousing
the captain back at camp.  You told him in no uncertain terms the urgency
of the situation, and he listened.  Of course, rousing the camp was not 
an instant manner, but it happened, you led them down the trail, and the
battle was joined.  Your decisive action lead to a solid victory.  The
\sMulanCountryPeople{} were totally blindsided.  It was your first taste
of real glory.

Or it should've been.  Your haste and decisiveness was key to the
successful action, and that victory lead to the discovery of further,
similar infiltration parties elsewhere on the border.  You helped turn
what could have been immense destruction and a long, bloody war into a
strong and decisive campaign for \sHomeCountry{}.  So, why did
\cMulan{\first} get all the credit?  All anyone seemed to remember was
their bloody sword and their walk through the woods, none of your sprint
or ability to discern the almost-invisible trail they left on an
overcast night.  And you accounted for yourself well in the brief
battle, too.  But \cMulan{\first}'s the one who gets proclaimed a
hero, who gets a feast in their honor back at the fort, who gets a
personal visit from the monarch and proclaimed a General of the
Armies.  You, you're just a footnote, a sidekick, an assistant.  A
lieutenant.

You trusted \cMulan{\first} as an ally, and now they're basking in all
the honor and you're just following along as an afterthought.  You wouldn't
have put it past them to even neglect to bother putting you on the Fire
delegation to the Convergence.  There are so many important people
here.  There must be some way to show that you're the real hero, or at least
that \cMulan{\first} doesn't deserve all this outrageous treatment.  You'd
love to take them down a peg or two.  Of course, if you let their secret out,
yours might come out too, and that would just be adding more humiliation.
So you have to be clever.  But clever has always been your strong suit.

Meanwhile, this is the Convergence, and it's a prime opportunity to
keep those frail little aristocratic Air artists and the greedy
worthless Water brokers from selling out \sHomeCountry{} in the name
of ``peace'' and ``prosperity''.  You know that for \sHomeCountry{} to get
the respect and position it deserves, you need to be known for your
strong military.  And that's why it's important to overturn this absurd
prohibition against the use of fire magic in warfare.  War's for real, not
some sort of spectator event.  Only a fool goes to a fight without
the best weapons available.

And, of course, the Realignment brings the opportunity to move the
Fire caste, and thus the military, to the top of the heap.  Military
leadership means more resources for the army, a stronger country, and
a position for expansion.  More wars means more opportunity for glory.
You know that \sHomeCountry{} could show the world, if those weak
nancy pansy artists weren't holding it back.  But with Fire in charge,
they wouldn't be able to.

(Of course, not \emph{actually} being Fire clan, you'll need to get
two Water gems and make a Water butterfly without letting your secret out.
But that shouldn't be too hard if you keep your wits about you.)

Every battle hinges on a key point of decision.  This Convergence may
not be a true battle of blood and glory, but it's a point of decision
nevertheless.  Make sure \sHomeCountry{} chooses the right path, and one
way or another, you'll get the glory you deserve.

\begin{itemz}[Goals]
\item Find a way to show up \cMulan{} and get the recognition you deserve.
\item Ensure that \sHomeCountry{} allows the use of fire magic in to enhance
  your combat superiority.
\item Move Fire to the top in the Realignment to turn \sHomeCountry{}'s
  focus away from silly frivolities and towards showing the rest of the world
  our superiority through war.
\item If Fire does switch places with Air, then you should convince \cRoyalty{} to select you and not \cMulan{} as the new ruler of \sHomeCountry{}.
\end{itemz}

\begin{contacts}
\contact{\cMulan{}} Your best friend among the Fire soldiers.  Secretly
Earth caste.  They got lauded as a hero after the two of you stopped
the \sMulanCountryPeople{} and their subterfuge, and didn't seem to mind
your contributions getting ignored.
\contact{\cRealPriest{}} The third member of the Fire delegation.  Supposedly
an excellent soldier.
\contact{\cHotPerson{}} An exceedingly attractive noble of the Air caste. Even with all that's going on today, perhaps you could find some time to get to know them better\ldots{}
\contact{\cGuildmaster{}} The leader of the Water caste. Awfully pompous and self-important for someone who is quite content with the safe life of a merchant.
\end{contacts}

\end{document}
