\documentclass[char]{iron}
\begin{document}
\name{\cMulan{}}

They told you you were worthless.  That a little Earth dirtgrubber would never
amount to anything.  But you proved them wrong.  Oh, if they could see you now.

You were born to the Earth caste.  A poor family of peasant farmers.
Air nobles owned the land; they got the lion's share of the harvest.
You were near the \sMulanCountry{} border, so you owed the Fire fort
nearby another portion.  And some piece of paper from your great
grandfather's day obligated you to supply some more to the post
station nearby, used by caravans and messengers.  What little was left
afterward was hardly enough to go around.  Still, your parents were
hard folk.  They knew how to scrape by.

The kids from the fort used to come by when their training for the day was
done and watch you, still hard at work in the fields with your sisters and
brothers.  They'd jeer at you.  Sometimes they'd throw rocks, particularly
if you were carrying a big bundle they could make you drop.  They called
you names, said you'd die in the dirt like the animal you were.  Your
siblings told you to ignore them.  You were never good at taking advice.
One time it got too much for you.  You yelled back that you were tougher
than they'd ever be, that they were weak stupid cowards, that you could
take any of them.  Of course, they weren't in the mood for a fair fight.
At least all they had were wooden training swords.  And as they left you
lying there, bloody and bruised, one of them said, ``You're just a pathetic
little earthworm.  You'd not worth a hundredth of one of us.  I'd like
to see you in a battle.  You'd die in seconds like a squealing pig.''

Your parents sat you down that night.  They said the same things they
always said, that there was honor in being Earth caste, that being at
the bottom of it all you could support all \sHomeCountry{}.  That it
was best for everyone if you knew your place and didn't try to upset
the balance.  Needless to say, you weren't in a mood to hear it.  You
weren't it that sort of mood at all.

You'd always been an clever kid.  You paid attention to the news
that'd come through the post station.  You'd heard about the concern
about relations with \sMulanCountry{}, the call for troops.  It wasn't
hard to sneak out at night, steal what you needed, and put together a
disguise.  In the morning, you showed up as \cMulan{\full, a young
  Fire soldier from an obscure branch of the \last} family, reporting
for duty.  If the sergeants noticed your unfamiliarity with the drills
or the poor fit of your armor, they chalked it up to growing up in the
capital, far away from the glory that was the proper Fire inheritance.
They praised your decision to come to the border and be what you
should be.

It was hard, of course.  Drills weren't as grueling as working in the
fields, but they used different muscles and took more precision.  And
in sparring, you had to go against people with years of experience on
you, and they weren't inclined to take it easy on this soft capital
newcomer.  But you were determined.  You knew you could be good
enough.  You practiced extra in the evenings, when the other soldiers
were off drinking or flirting.  And you got better.

There was another soldier there, about your age, that caught your attention.
They weren't like the other ones, who treated training like a game and worked
as little as they could get away with.  No, \cLieutenant{\intro} took practice
seriously, like you did.  You noticed them training alone in the evening,
once, and asked if they'd like to spar.  Soon, you were regular partners
for extra practice.  You could point out things for each other to work on and
encourage each other to keep pushing when weariness set in. But more importantly
than that, there was someone else here who didn't seem like an enemy.  Someone
that it felt like you could trust.

It was late some evening when you slipped.  You and
\cLieutenant{\first} were joking and chatting, catching your breath
after some intense sparring, when you told a story about something one
of your siblings had done out in the fields.  ``The fields?  I thought
you grew up in the capital.''  \cLieutenant{\first} asked.  You froze
for a moment, thinking of a story.  But then you hesitated.  You
really wanted to be able to trust someone, to not hide from everyone.
You \emph{thought} you could trust \cLieutenant{\first}.  And you decided
to go for it.  And guess what!  \cLieutentant{\first} was an outsider too!
A Water merchant who thought trade was weak and fighting was glorious!
After that, you two were tighter than tight.  You were fast friends, and
did everything together.

But then the simmering tensions with the \sMulanCountryPeople{} went hot.
There'd been attacks elsewhere on the border, and your division was sent out
to scout their movements.  You found an army camped on the other side of the
pass.  You set up camp in a defensible position and waited for orders to come
from the fort.  Orders were not fast in coming.

That night, while you were on guard duty, you heard signs of movement.
You wanted to go investigate, but the other guards told you it was
just an animal and wouldn't come.  \cLieutentant{\first}, though, was
with you.  And what did you find?  A division of
\sMulanCountryPeople{}, dressed in dark clothes, obviously trying to
sneak into \sHomeCountry{} to sabotage the supply lines or assassinate
the leaders!  You sent \cLieutentant{\first} to rouse your troops
while you tracked them from the shadows, leaving a trail for them to
follow.  You kept at it for an hour, constantly terrified of being
seen.  And then the troops arrived, and you all attacked.  The
\sMulanCountryPeople{} never knew what hit them.  Soon you stood
there, with your sword bloody and corpses at your feet, with your captain
looking at you with admiration.

The war has settled down, at least for now.  Now that they knew what
to look for, other forts caught several other detachments of
saboteurs, and the \sMulanCountryPeople{} soon backed down.
Overnight, you became the hero of the fort, of the whole army.  When
\cRoyalty{} themself came to the fort and made you a general,
crediting you with saving \sHomeCountry{} from destruction, you
thought it was a bit overdramatic, but you weren't going to say no.
You couldn't help but chuckle inwardly.  Worthless little earthworm,
eh?

And it's also, you guess, why you got picked as the leader of the Fire
delegation for the Convergence.  It's a great honor, you could hardly
refuse.  You made sure \cLieutenant{\first} got included as well, so
you'd have someone to talk to.  You don't really know the third delegate, \cRealPriest{\intro},  but you're told they have accounted themself well.

Becoming a hero overnight has brought you other kinds of attention,
too.  It's not exactly \emph{unwelcome} (you were never considered a
``catch'', before), but it is a bit bizarre, especially pursuit
from people such as this.  Your two most persistent
suitors are \cGuildmaster{\full}, Water Guildmaster and known for
their shrewd business dealings, and \cBastard{\full}, a well-off Air
aristocrat from a powerful family, and they've both been hinting that
marriage is on their minds.  You don't know quite what you think
of that, but it's nice to be pursued.  Currently, your leaning is towards
\cGuildmaster{}: a successful merchant seems a more honorable career
than an idle aristocrat, and you don't know what the aristocracy would
do if you were caught in an illegal marriage into a powerful family.  But
you're sure both of them will make great efforts to be your choice
at the Convergence.

As for the Convergence itself, there are three matters of importance.
First, the alliance with \sTreatyCountry{}.  You've seen the harshness
of war firsthand.  A strong defensive alliance would help protect
\sHomeCountry{} and hopefully avoid the need for further fighting.
Second, the use of magic in warfare.  Even though your caste proposed
the question, you have your reservations.  You've seen how hard war is
on the common people when fields and towns turn into battlefields.  Fire
magic is amazingly destructive; adding it to the mix would destroy the
land you fight over more thoroughly and invite similarly harsh tactics
from your foes in response.  No, adding the destruction of elemental flame
to your arsenal is a slope you don't want to go down.

And last, of course, there is
the Realignment.  You know how hard things were growing up, how hard they must
still be for your family.  How hard the Earth caste works and how little
they get for it, while Water merchants rake in gold without actually
producing anything of value.  Moving Earth above Water would move those
who feed and clothe the country a little closer to the place they deserve.

Of course, to make your contribution to the Realignment you're going
to need to trade for some different gems, particularly the two Earth
gems you need.  At first you were worried about someone noticing that
you're not actually Fire caste, what with the gems and all, but then
you thought about it some more.  You've proven yourself, that much is
clear.  But it doesn't mean as much if no one knows who you really
are, that the hero who saved a country is actually Earth caste.  After
the Realignment is over, if you can find a suitably dramatic
opportunity, maybe it's time to reveal the truth, to everyone.  It's
terrifying, to be honest.  You could lose your position, be forced
back into your old life, or worse.  And who knows what your suitors
would do if they found out the truth.  But, you're not really in this
just for yourself any more.  You want to make \sHomeCountry{} a better
place, to keep future Earth children from having to go through what
you did.  And that's not going to happen if you just play it safe.

Hopefully the gods of Earth are still smiling on you.  You're going to
need all the help you can get.

\begin{itemz}[Goals]
\item Use the Realignment to move Earth above Water, to make life a little
  less harsh for your family and caste.
\item Ensure that the alliance with \sTreatyCountry{} goes through,
  for greater protection.
\item Ensure that the prohibition on fire magic in combat is maintained.
\item Find a suitably dramatic opportunity, ideally post-Realignment,
  to reveal that the ``hero who saved \sHomeCountry{}'' is actually Earth caste.
\item Figure out what to do about your romantic situation. If you \emph{do} choose to marry, there is no more auspicious time than immediately after the Realignment\ldots{}
\end{itemz}

\begin{contacts}
\contact{\cLieutenant{}} Your friend among the Fire soldiers, the only one
who knows your secret.  Secretly Water caste.
\contact{\cRealPriest{}} The third member of the Fire delegation, a soldier
of distinction.
\contact{\cRoyalty{}} The ruler of \sHomeCountry{}.  If you'd been told
a year ago that you'd be honored by the likes of them\ldots{}
\contact{\cGuildmaster{}} One of your suitors, the Guildmaster of the Water caste.
\contact{\cBastard{}} Your other suitor, a well-bred noble of the Air caste. You do have some feelings for them---but if you were to reveal your true identity, a romance with \cBastard{} could never be.
\contact{\cHotPerson{}} An extraordinarily attractive Air noble who has recently caught your eye. Perhaps it would be hasty to limit your options to just \cGuildmaster{} and \cBastard{}\ldots
\end{contacts}

\end{document}
