\documentclass[sheet]{iron}

\begin{document}

\name{GM Instructions}

\section{Materials Needed}

\begin{itemz}[Iron GM Base Materials]
\item 12 origami butterflies, 3 each of four different colors (one per element)
\item 12 large envelopes for character packets
\item 12 smaller envelopes to put the butterflies in
\item Scissors
\item A sharpie to label character packets
\end{itemz}

\begin{itemz}[Additional Materials]
\item 60 flat glass marbles, beads, or other tokens to represent elemental
  gems, 15 in each color
\item Scotch tape
\end{itemz}

\section{Printing and Production}

\begin{itemize}
\item Print out the included documents: one copy each of
  \texttt{listchar-PRINT.pdf} and
  \texttt{butterflies.pdf}, and 15 copies each of
  \texttt{rules-scenario.pdf} and \texttt{whos-who.pdf}.
\item Additionally, print one copy of
  \texttt{stickeritem-PRINT.pdf}. It's designed to be printable on
  2'' by 4'' stickers, but you can also print it on ordinary paper
  and cut out the labels.
\item If you would like appropriately-colored namebadges, print 
  \texttt{badge-PRINT-air.pdf}, 
  \texttt{badge-PRINT-fire.pdf}, 
  \texttt{badge-PRINT-water.pdf}, 
  \texttt{badge-PRINT-earth.pdf}, and
  \texttt{badge-PRINT-foreigner.pdf} on appropriate colors of cardstock.
  Otherwise, just print \texttt{badge-PRINT.pdf}.
\item Put each character sheet in a large envelope and label the
  envelope with the character name.
\item Stick or tape each envelope label (``So-and-so's spirit
  butterfly'') to a small envelope.  Put a butterfly of the color
  corresponding to the gem the label requires the most of in the
  envelope and close it.  Put each envelope in the character packet
  indicated on the label.
\item Cut out each badge, noting which packet the badge goes in by the
  ``previously'' header on some badges, and put the badge in the proper packet.
\item Look at the ``Notables at the Convergence'' sheet and give 5 elemental
  gems to each character of the color corresponding to the delegation they
  are in.  (Thus, their apparent caste, as opposed to butterflies, which
  are by actual elemental affinity.)
\item Put the ``Butterfly Placement Area: Move Earth above all other castes''
  sheet in \cRoyalty{\full}'s packet, and keep the other Butterfly Placement
  Areas aside.
\item Keep the rules sheets and these ``Notables at the Convergence'' sheets
  separate, as piles for players to pick up as they arrive.
\end{itemize}

\section{Setup and Running}

\begin{itemize}
\item Set up the remaining Butterfly Placement Areas in obvious locations,
  for voting on the Realignment.
\item As players arrive, assign them a character packet and give them
  a copy of the rules and the ``Notables at the Convergence'' sheet.
\item After players have had time to read their sheets, start game.
\item Set a timer to keep the game on schedule: remind players to vote
  on Questions 45 minutes in (but ideally let \cRoyalty{\full} or
  \cFakePriest{\full} run the actual voting), and resolve the
  Realignment 60 minutes in.  End game after an hour and a half, but
  feel free to fudge this slightly based on player mood.
\item Aside from the schedule, this game should not require particular
  GM intervention.  Don't let anyone accomplish anything beyond flavor with
  magic, violence, or leaving the Temple.  There's nothing physically
  preventing characters from leaving, but discourage players from doing
  so because staying in game is more fun.
\item Keep wrapup short, giving each character at most a few moments to
reveal any remaining secrets.
\end{itemize}

\section{Characters to Cut}

If you need to cut characters, cut characters from the bottom of this list
up.  (Game is best run with all 12 characters, and shouldn't run at all
with fewer than 5.)  If you cut characters, give additional elemental gems to
\cRoyalty{\full} as indicated next to the last character you didn't cut
so there are enough gems in game for everyone
to summon their spirit butterfly.

\begin{enum}
\item \cRoyalty{\full}
\item \cMulan{\full}
\item \cGuildmaster{\full}
\item \cSpy{\full}
\item \cFakePriest{\full} (one air, two fire, one earth)
\item \cLieutenant{\full} (two air, two earth)
\item \cHotPerson{\full} (four earth)
\item \cRealPriest{\full} (one water, five earth)
\item \cServant{\full} (one air, two water, one earth)
\item \cPatriot{\full} (two air, three water)
\item \cBastard{\full} (four water)
\item \cTrickster{\full}
\end{enum}

\section{Plot Overview}

The basic plot is pretty straight-forward.  There are the three Questions,
each of which starts with two people in favor and two people against.
None of these Questions have any in-game effect.

There's also is the Restructuring, which everyone has an opinion on:
three people in favor of each of the possible swaps,
\cFakePriest{\full} favoring the status quo, \cTrickster{\full} just
going for what will cause the most chaos, and \cRoyalty{\full} having
a secret extra option to move the Earth caste right to the top.
There's no way to add other options to the Restructuring;
\cRoyalty{}'s thing is something they put a lot of work into figuring
out pregame.  The only in-game effect of the Restructuring is to
change what marriages are legal, but hopefully players will play up
the new social order.

There's a lot of disguises and forbidden romance and mistaken
identity, but hopefully that'll mostly take care of itself.  Encourage
people to play up the ridiculousness and not take keeping their
secrets too seriously.

\subsection{Setting Truths}

There are some setting details that not everyone starts off knowing but
also aren't big secrets, that you can reveal in response to player questions
at your discretion.

\begin{itemize}
\item At the last Convergence, 100 years ago, nothing changed in the
  Restructuring.
\item The marriage prohibitions are based on your actual caste, not
  your apparent caste, and no proper cleric would marry someone they
  thought was lying about their caste.
\item Elemental gems are a naturally-occurring resource mined in \sHomeCountry{}
  and found nowhere else.
\item Many people of various castes have some ability to use magic of the
  appropriate element, but in general magic takes a lot of preparation,
  so no one's expecting anyone to be doing anything significant with it today.
\item The religion in \sHomeCountry{} believes in gods, elemental spirits
  and saints, but most people have never encountered any of these themselves.
\item Other countries don't have castes or elemental magic the way \sHomeCountry{} does.
\item The other countries are in favor of \sHomeCountry{} exporting elemental gems and oppose the use of magic in warfare.  \sTreatyCountry{} is in favor of the alliance, whereas the other neighboring countries (chiefly \sMulanCountry{}, the country that tried to invade, and \sSpyCountry{}) oppose it.
\end{itemize}

\end{document}
